An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-07-01 background.tex
Updates from Overleaf

\begin{definition}[Step]\label{def:cosim_step}
  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
  and $i$ denoting the order of the function call.
\end{definition}

@@

\begin{definition}[Algebraic loops] 
An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
A strongly connected component: $SCC = v \in V: Path(v,v)$\\
$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
\todo{Claudio check this definition and add a formalization of the challenge introduced}
\end{definition}

\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
The algebraic dependency will lead to the following difference between performing to following :
\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
\end{definition}

@@

The initialization of the system requires the application of fixed point iteration, as defined by \cref{def:fixedpoint}.
\begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $\LoopVariables \neq \emptyset$.\\
Fixed point iteration should be used by 
$\forall v \in \LoopVariables $

\end{definition}

>>>>

\begin{definition}[Step]\label{def:cosim_step}
  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup \bigcup_{l \in \loops} \fixedpoint_{l},$
  and $i$ denoting the order of the function call. Fixed point is defined in \cref{def:fixedpoint} and loops in \cref{def:loops}
\end{definition}

@@

\begin{definition}[Algebraic loops]\label{def:loops}
An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
A strongly connected component: $SCC = v \in V: Path(v,v)$\\
$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
\todo{Claudio check this definition and add a formalization of the challenge introduced}
\end{definition}

\begin{definition}[Fixed Point Iteration]\label{def:fixedpoint}
The fixed point iteration $\fixedpoint_{Loop}$ of a given algebraic loop is the ordered sequence of all FMU functions call $\functioncall$ performed on the variables in the algebraic loop.
$\fixedpoint_{l} = $ 
\end{definition}

\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
The algebraic dependency can lead to 
\end{definition}

@@
